---
title: "PSY 8960 Week 8 Project"
author: "Vivien Lee"
date: `r Sys.Date()`
output: 
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../out/")
  })
---


# **Reproducible Image and Online Resources**
[Insert plain text explanation]
An image of this project as of date can be accessed by clicking this link.



# **Script Settings and Resources**
```{r setup, message = FALSE}
# Loading all required libraries
library(tidyverse)
library(ggplot2)
```


# **Data Import and Cleaning**
For this section, using a single series of pipes, I cleaned the data by reverse coding Q5 (instead of doing it directly on csv file to ensure reproducibility), casted variables into their correct types, and computed the mean of Q1-Q6 as well as mean of Q8-Q10 for creating data visualization below. 
\n
```{r cleaning, message= FALSE}

week8_tbl = read_csv("../data/week3.csv") %>% 
  tibble() %>% 
  mutate(q5 = 6 - q5,
         gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")),
         timeStart = ymd_hms(timeStart),
         timeEnd = ymd_hms(timeEnd)) %>% 
  rowwise() %>% 
  mutate(mean_1_to_6 = mean(c(q1,q2,q3,q4,q5,q6)),
         mean_8_to_10 = mean(c(q8,q9,q10))) %>% 
  ungroup()
```


# **Visualization**
I created a scatterplot using ggplot() and used geom_smooth() to create a regression line, leaving se = TRUE (default) to retain the shaded error band. There appears to be a weak relationship between the two means.

\n
```{r visualizations, echo = FALSE, message = FALSE, fig.align= "center"}

week8_tbl %>% select(paste0("q",1:6))

# Scatterplot
week8_tbl %>%
  ggplot(aes(x = mean_1_to_6, y = mean_8_to_10)) + 
  geom_point() + 
  geom_smooth(method = "lm", color = "purple") + 
  labs(x = "Mean scores on Q1-Q6",
       y = "Mean scores on Q8-Q10")
```


# **Analysis** 
The code below computes the correlation between mean of Q1-Q6 and mean of Q8-10. I observed a correlation of `r cor.test(week8_tbl$mean_1_to_6,week8_tbl$mean_8_to_10)$estimate` with a p-value of `r cor.test(week8_tbl$mean_1_to_6,week8_tbl$mean_8_to_10)$p.value` > 0.05. Using the threshold of $\alpha$ = .05, the correlation between the mean of Q1-Q6 and mean of Q8-Q10 are not statistically different from zero. 

\n
```{r analysis}
cor_result = cor.test(x = week8_tbl$mean_1_to_6, y = week8_tbl$mean_8_to_10)
```


# **Data Export** 
In this final step, I exported the cleaned dataset as an RDS object to retain properties (e.g., types) of the dataset and saved it into the shiny_week8 directory for shiny app to use. 
```{r export}
week8_tbl %>% saveRDS(file = "../shiny_week8/week8_shiny_data.rds")
```









